dwctaxon, an R package for editing and validating taxonomic data in Darwin Core format

### 2023-12-15 ms.Qmd
Update MS based on input from WI
Fix rOpenSci capitalization

The `dwctaxon` R package provides functions to edit and validate taxonomic data in compliance with the widely used Darwin Core (DwC) standard [@Wieczorek2012] for biodiversity data.
`dwctaxon` automates several data editing steps, thereby simplifying workflows and decreasing the chance of human-generated data entry errors.
Furthermore, it conducts automated checks to validate taxonomic datasets, thereby alerting database maintainers to problems as soon as possible.
`dwctaxon` will accelerate the generation and maintenance of taxonomic data, a critical part of the effort to document and conserve earth's biodiversity.
`dwctaxon` has passed [code review](https://github.com/ropensci/software-review/issues/574) at [ROpenSci](https://ropensci.org/).
Complete documentation is available at <https://docs.ropensci.org/dwctaxon> and source code is available at <https://github.com/ropensci/dwctaxon>.

@@

Taxonomic data are frequently being updated due to, for example, discovery of new species or revision of existing taxonomic concepts.
These taxonomic changes can be complicated.
For example, changing the status of one name to the synonym of another could potentially involve modifying many other names if they are synonyms of the first.
Because of these properties, maintaining a taxonomic database in compliance with DwC can be onerous and error-prone if done by hand, especially if the database is large.
There is therefore a need for software to automate entry and validation of DwC taxonomic data.

@@

Members of the Iwasaki Lab (The University of Tokyo) provided helpful comments while the package was in development.
This was research supported in part by Japan Society for the Promotion of Science (Kakenhi) grant no. 16H06279, 22H04925 and 22K15171.
Thanks to Collin Schwantes and Stephen Formel for reviewing the code and Noam Ross for handling the code review process at ROpenSci.

>>>>

The `dwctaxon` R package provides functions to edit and validate taxonomic data in compliance with the widely used Darwin Core (DwC) standard [@Wieczorek2012] for biodiversity data.
`dwctaxon` automates several data editing steps, thereby simplifying workflows and decreasing the chance of human-generated data entry errors.
Furthermore, it conducts automated checks to validate taxonomic datasets, thereby alerting database maintainers to problems as soon as possible.
`dwctaxon` will accelerate the generation and maintenance of taxonomic data, a critical part of the effort to document and conserve earth's biodiversity.
`dwctaxon` has passed [code review](https://github.com/ropensci/software-review/issues/574) at [rOpenSci](https://ropensci.org/).
Complete documentation is available at <https://docs.ropensci.org/dwctaxon> and source code is available at <https://github.com/ropensci/dwctaxon>.

@@

Taxonomic data are frequently updated due to, for example, discovery of new species or revision of existing taxonomic concepts.
These taxonomic changes can be complicated.
For example, changing the status of one name to the synonym of another could potentially involve modifying many other names if they are synonyms of the first.
Because of these properties, maintaining a taxonomic database in compliance with DwC can be onerous and error-prone if done by hand, especially if the database is large.
There is therefore a need for software to automate entry and validation of DwC taxonomic data.

@@

Members of the Iwasaki Lab (The University of Tokyo) provided helpful comments while the package was in development.
This was research supported in part by Japan Society for the Promotion of Science (Kakenhi) grant no. 16H06279, 22H04925 and 22K15171.
Thanks to Collin Schwantes and Stephen Formel for reviewing the code and Noam Ross for handling the code review process at rOpenSci.
